curacao_threeplayers_rest_monster

### 2020-09-29 inst/curacao1962_threeplayers_rest_monster.Rmd
lower-level (Fisher) analysis of rested players

  white_player_rested <- a[i,5] - a[i,6] > 0
  black_player_rested <- a[i,6] - a[i,5] > 0

@@

>>>>

  white_player_rested <- a[i,5] - a[i,6] > 1
  black_player_rested <- a[i,6] - a[i,5] > 1

@@

```{r}
table(a[,3],a[,5]-a[,6])
```

A bit of tidying:

```{r}
aa <- subset(a,a[,5] != a[,6])
aa <- subset(aa,aa[,3] != "1/2-1/2")

M <- table(aa[,3],white_rested=aa[,5]<aa[,6])
M
fisher.test(M,alternative="greater")
```
